\tealeaves: an R package for modelling leaf temperature using energy budgets

### 2019-07-23 ms/ms.Rnw
revised Discussion

% paragraph 2: leaf energy budgets are commonly used tools to model leaf temperature
To understand leaf thermal physiology, plant scientists need mathematical and computational tools to model leaf temperature as a function of leaf traits and the environment. Balancing energy budgets is a powerful mathematical tool for understanding how leaf traits and environmental parameters influnce plant physiology that has been used for over a century \citep{Raschke_1960}. The equilibrium leaf temperature is that in which the energy gained from incoming solar and infrared radiation is balanced by thermal infrared radiation losses, sensible heat loss/gain, and latent heat loss through evaporation \citep{Gutschick_2016}. Leaf angle, size, and conductance to water vapour alter leaf temperature by changing how much solar radiation they intercept and how much heat they lose through sensible and latent heat flux. Likewise, enrvironmental factors such as sunlight, air temperature, humidity, and wind speed influence heat transfer between leaves and the surrounding microclimate \citep{Gutschick_2016}. Hence, leaf energy budget models can offer deep insight on plant thermal physiology by asking how temperature is affected by one factor in isolation or in combination with another.

@@

% Comparison with other appraoches
The \tealeaves~model is more complex than most other leaf energy balance models in the literature, which makes it more flexible and realistic but more computationally intensive. For example, the R package \pkg{plantecophys} \citep{Duursma_2015} uses the isothermal net radiation approximation of \citeauthor{Leuning_etal_1995} (\citeyear{Leuning_etal_1995}) to reduce the number of iterations and hence speed up computation. The main difference is that more complex approaches correct for atmospheric stability when calculating boundary layer conductance (\cite{Webber_etal_2017}; see Eqns \ref{eq:GrRe} -- \ref{eq:Tv}). Other studies simplify and speed up the model further by ignoring free convection \citep{Buckley_etal_2014}. These simplifications may be adequate for many applications and the benefit in speed may be necessary for scaling up. However, recent comparisons of simple and complex energy balance models in the field found that the complex models, like that implemented in \tealeaves, fit the observed distribution of wheat leaf canopy temperatures better \citep{Webber_etal_2017}. Future development of \tealeaves~will make it easier and faster to implement simpler models. A full range of models, from simple to complex, will serve the broadest range of applications and allow users to test when simplifying assumptions are justified. To facilitate this, future versions of \tealeaves~will allow users to provide functions rather than values for some parameters. A less computationally intensive model could be contructed by substituting simpler functions (e.g. instead of Eqns \ref{eq:GrRe}--\ref{eq:Tv}). Or users could substitute a more appropriate function for their application, such as cloudy rather than clear skies in the case of Eqn. \ref{eq:Tsky}.

@@

\begin{equation}
  S_\mathrm{r} = 2 \sigma \alpha_\mathrm{l} T_\mathrm{air} ^ 4.
\end{equation}

>>>>

% paragraph 2: leaf energy budgets are commonly used tools to model leaf temperature
To understand leaf thermal physiology, plant scientists need mathematical and computational tools to model leaf temperature as a function of leaf traits and the environment. Balancing energy budgets is a powerful mathematical tool for understanding how leaf traits and environmental parameters influnce plant physiology that has been used for over a century \citep{Raschke_1960}. The equilibrium leaf temperature is that in which the energy gained from incoming solar and infrared radiation is balanced by thermal infrared radiation losses, sensible heat loss/gain, and latent heat loss through evaporation \citep{Gutschick_2016}. Leaf angle, size, and conductance to water vapour alter leaf temperature by changing how much solar radiation they intercept and how much heat they lose through sensible and latent heat flux. Likewise, enrvironmental factors such as sunlight, air temperature, humidity, and wind speed influence heat transfer between leaves and the surrounding microclimate \citep{Gutschick_2016}. Under controlled conditions, leaf energy budget models are highly accurate \citep{Schymanski_Or_2017}. Hence, they can offer deep insight on plant thermal physiology by asking how temperature is affected by one factor in isolation or in combination with another.

@@

% Comparison with other appraoches
The \tealeaves~model is more complex than most other leaf energy balance models in the literature, which makes it more flexible and realistic but more computationally intensive. For example, the R package \pkg{plantecophys} \citep{Duursma_2015} uses the isothermal net radiation approximation of \citeauthor{Leuning_etal_1995} (\citeyear{Leuning_etal_1995}). This reduces the number of iterations and speeds up computation by assuming that longwave radiative flux from the leaf is proportional to air rather than leaf temperature. Other recent models \citep[e.g.][]{Buckley_etal_2014, Schymanski_Or_2017} assume free convection or do not account for virtual temperature differences in moist air (Eqn. \ref{eq:Tv}) \citep{Okajima_etal_2012, Duursma_2015}. Other models, except \citeauthor{Okajima_etal_2012} \citeyear{Okajima_etal_2012}, also do not account for different surrounding temperatures above and below the leaf surface ($T_\mathrm{sky}$ and $T_\mathrm{air}$, respectively) when calculating thermal infrared radiation (see Eqn \ref{eq:Tsky}). These simplifications may be adequate for many applications and the benefit in speed may be necessary for scaling up. However, recent comparisons of simple and complex energy balance models in the field found that the complex models, like that implemented in \tealeaves, fit the observed distribution of wheat leaf canopy temperatures better \citep{Webber_etal_2017}. Future development of \tealeaves~will make it easier to implement simpler models. A full range of models, from simple to complex, will serve the broadest range of applications and allow users to test when simplifying assumptions are justified. To facilitate this, future versions of \tealeaves~will allow users to provide functions rather than values for some parameters. For example, a less computationally intensive model could be contructed by using a function for calculating boundary layer conductances that assume free convection is negligible. Or users could substitute a more appropriate function for their application, such as cloudy rather than clear skies in the case of Eqn \ref{eq:Tsky}.

@@

\begin{equation}
  S_\mathrm{r} = 2 \sigma \alpha_\mathrm{l} T_\mathrm{leaf} ^ 4.
\end{equation}
